---
title: "w241_final_project"
author: "Armand Kok"
date: "December 2, 2018"
output: pdf_document
---
```{r setup, include=FALSE}}
# load packages 
library(foreign)
library(data.table)
library(foreign)
library(tidyr)
library(lmtest)
library(sandwich)
library(multiwayvcov)
```


# TODOs
* remove users who participate in both studies



```{r}
mydir <- 'C:/Users/ak021523/Documents/GitHub/mids-repos/W241/w241_Final_Project/'

#load data
d <- read.csv(paste0(mydir,'clean_data.csv'))
d <- data.table(d)
head(d)
```

# Data Exploration

## group

Look at the number of treatment and control, make sure that they're even. 200 responses were requested, however there are 227 responses in total, so it looks like some people clicked through multiple times

```{r}
group_dt <- d[,list(observations = .N), by = list(phase, group),]
group_dt[order(phase, group)]
```

## finished

It looks like there are about twenty people who did not finish, these folks will be filtered out.

```{r}
paste('Number of people who did not finish the survey:', nrow(d[d$finished == FALSE,]))

#filter out people who did not finish the surveys
d <- d[d$finished == TRUE,]
```

## Never Takers

The never takers are the people who spends less than 30 seconds in the article page, or people who answers the comprehension question with  "Tuberculosis can be treated with diet of gummy bears and diet soda", Tuberculosis is no longer a health issue", and "Kevin P can wipe out tuberculosis in his free time"

```{r}
d$nt_ind <- (d$time_submit_article < 30 | 
             d$point_of_article == 'Tuberculosis is no longer a health issue.' |
             d$point_of_article == 'Tuberculosis can be treated with diet of gummy bears and diet soda')


d$complier_ind <- (d$nt_ind != TRUE)
```

In the placebo test, there were around 16 never takers in the control group, and 14 never takers in the treatment group.

```{r}
#never takers in each group
nt_control <- nrow(d[d$nt_ind == 1 & d$group == 'Control' & d$phase == 'Placebo Test',])
nt_treatment <- nrow(d[d$nt_ind == 1 & d$group == 'Treatment' & d$phase == 'Placebo Test',])

#print out the number of never takers in each group
paste('Never Takers in Control:', nt_control)
paste('Never Takers in Treatment:', nt_treatment)
```

In the primary experiment there are around 13 never takers in the control group, and about 28 never takers in the treatment group.

```{r}
#never takers in each group
nt_control <- nrow(d[d$nt_ind == 1 & d$group == 'Control' & d$phase == 'Primary',])
nt_treatment <- nrow(d[d$nt_ind == 1 & d$group == 'Treatment' & d$phase == 'Primary',])

#print out the number of never takers in each group
paste('Never Takers in Control:', nt_control)
paste('Never Takers in Treatment:', nt_treatment)
```

## worker_id

```{r}
dupe_dt <- d[,list(observations = .N), by = list(worker_id),]
dupe_dt[dupe_dt$observations > 1,]
```

```{r}
d[d$worker_id == 'A1CPVTZAK27YSF',]
d[d$worker_id == 'A2AAG78CGKX2U5']
```

## political_identification

Binarize political identification

```{r}

df <- data.table(d$political_identification)
df <- data.table(model.matrix(~ . + 0, data=df, contrasts.arg = lapply(df, contrasts, contrasts=FALSE)))

d$republican <- df$V1Republican
d$democratic <- df$V1Democratic
d$independent <- df$V1Independent
```


## gender

Binarize the gender

```{r}
df <- data.table(d$gender)
df <- data.table(model.matrix(~ . + 0, data=df, contrasts.arg = lapply(df, contrasts, contrasts=FALSE)))

d$female <- df$V1Female
```

## age

Binarize the age categories

```{r}
df <- data.table(d$age)
df <- data.table(model.matrix(~ . + 0, data=df, contrasts.arg = lapply(df, contrasts, contrasts=FALSE)))

d$age_18_24 <- df$`V118-24`
d$age_26_35 <- df$`V126-35`
d$age_36_48 <- df$`V136-48`
d$age_49_59 <- df$`V149-59`
d$age_59_older <- df$`V159 or older`
```

# Placebo Test

```{r}
#partition placebo data
placebo_dt <- d[d$phase == 'Placebo Test',]
```

## ITT Calculation

```{r}
#ITT calculation
model_one <- lm(article_effectiveness ~ group, data = placebo_dt)
coeftest(model_one, vcovHC)
```

```{r}
itt <- mean(placebo_dt[placebo_dt$group == 'Treatment',]$article_effectiveness)-
       mean(placebo_dt[placebo_dt$group == 'Control',]$article_effectiveness)
```


## CACE Calculation

```{r}
#CACE one
cace_one <- lm(article_effectiveness ~ group, data = d[d$phase == 'Placebo Test' & d$nt_ind == 0,])
coeftest(cace_one, vcovHC)
```


```{r}
cace <- mean(placebo_dt[placebo_dt$group == 'Treatment' 
                        & placebo_dt$nt_ind == 0,]$article_effectiveness) - 
        mean(placebo_dt[placebo_dt$group == 'Control' 
                        & placebo_dt$nt_ind == 0,]$article_effectiveness)
paste(cace)
```

# Primary

```{r}
#partition placebo data
primary_dt <- d[d$phase == 'Primary']
```

## article effectiveness outcome

```{r}
cace_model <- lm(article_effectiveness ~ group, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(cace_model, vcovHC)
```

```{r}
#TODO: add a regression model that have interaction term with political_identification
mv_cace_model <- lm(article_effectiveness ~ group + age_18_24 + age_26_35 + age_59_older + age_49_59 + female + democratic + republican, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(mv_cace_model)
```

## support_tb
```{r}
cace_model <- lm(support_tb ~ group, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(cace_model, vcovHC)
```

```{r}
mv_cace_model <- lm(support_tb ~ group + age_18_24 + age_26_35 + age_59_older + age_49_59 + female + democratic + republican, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(mv_cace_model)
```

## recommend_article

```{r}
cace_model <- lm(recommend_article ~ group, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(cace_model, vcovHC)
```

```{r}
mv_cace_model <- lm(recommend_article ~ group + age_18_24 + age_26_35 + age_59_older + age_49_59 + female + democratic + republican, data = primary_dt[primary_dt$complier_ind == 1])
coeftest(mv_cace_model)
```
